Limited evidence for widespread heterogeneity in psychology

### 2018-07-02 writing/appendixA-heterogeneity.rmd
Updated Appendix A

@@

In our main results we simulated data to estimate type I error and power using an average effect size of zero. As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity. However, as a sensitivity analysis we in the Appendix analyze the same data, but generated with an average 'medium' effect size as defined by Cohen (1988).

@@

_Type I error and power for data with an average 'medium' effect size_
```{r table_results}
dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
names(dens) <-  sort(unique(dat$effect))

#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
I2_ci_lb <- dens %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')
```

```{r}
knitr::kable(I2_ci_lb, digits = 2)
```

Some comments on type I errors and power in Table A1.Subsequently comments on Figure A1.

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("../data/appendixA_tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales') #effects that were transformed from OR to SMD

#Categorize effects by type of simulation for graphing
effect_type <- distinct(select(dat, effect, effect_type)) %>% 
  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | 
                                effect_type == "Raw mean difference", "MD", effect_type),
         effect_type = recode(effect_type, "d" = 'SMD',
                              "r" = "Fisher's z"))

dat3 <- dat3 %>% 
  bind_rows(.id = "effect") %>% #create dataframe with identifier
  left_join(., effect_type) %>% 
  select(I2, tau, effect, effect_type) %>% 
  group_by(tau, effect, effect_type) %>% 
  summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
  ungroup()

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black"))

```

_Figure A1._

Here some comments on Figure A2.
```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("../data/appendixA_power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

#Simulated data at various heterogeneity levels, prep for plotting
I2_dist <- dens %>% 
  bind_rows(.id = "effect") %>% 
  rename(Heterogeneity = tau_index) %>% 
  mutate(Heterogeneity = recode(Heterogeneity,
                            '1' = "Zero",
                            '2' = "Small",
                            '3' = "Medium",
                            '4' = "Large"),
         Heterogeneity = as.factor(Heterogeneity))

#Observed I2 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'est_heterogeen_smd_raw'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, I2 = s_I2) %>%
  mutate(Heterogeneity = "Observed")

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = "")))

```

_Figure A2._

Finally, conclusions from sensitivity analysis.

>>>>

```{r results}
##Zero effect size results
dens <- readRDS("../data/power_simulation_results.RDS") 
names(dens) <-  sort(unique(dat$effect))

#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
zero <- dens %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4') %>% 
  select(-effect)

##Medium effect size results
dens2 <- readRDS("../data/appendixA_power_simulation_results.RDS") 
names(dens2) <-  sort(unique(dat$effect))

#Summary of results.
medium <- dens2 %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')

##combine for table

comparison <- cbind(zero, medium)
```

@@

In our main results we simulated data to estimate type I error and power using an average effect size of zero. As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity. However, as a sensitivity analysis we in this Appendix again estimate type I error and power, but generated with an average 'medium' effect size as defined by Cohen (1988).

Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs. medium are shown for each effect in Table A1. In both cases type I error is consistently conservative, as compared to the expected 5% error rate. With a an effect size of zero, average power was `r 100*round(mean(zero$small), digits = 2)`/`r 100*round(mean(zero$medium), digits = 2)`/`r 100*round(mean(zero$large), digits = 2)`% for small/medium/large heterogeneity respectively. The corresponding power with an average effect size was `r 100*round(mean(zero$small), digits = 2)`, `r 100*round(mean(zero$medium), digits = 2)`, and `r 100*round(mean(zero$large), digits = 2)`%. To conclude, changing true effect size in our simulations from zero to medium has little impact on estimated type I error and power.

@@

_Type I error and power for data with a true effect size of zero vs. 'medium'_

```{r}
knitr::kable(comparison, digits = 2)
```

**Note.** Column headers indicate the degree of simulated heterogeneity where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively. Code to reproduce table: osf.io/bsjhu/
